%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,letter,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{424242}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Marie-H.}{Monfils}


\email{\href{mailto:marie.monfils@utexas.edu}{\nolinkurl{marie.monfils@utexas.edu}}}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{publications}{%
\section{Publications}\label{publications}}

\hypertarget{journal-articles}{%
\subsection{Journal Articles}\label{journal-articles}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-1Monfils_2022}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Monfils, M.-H., \& Domjan, M. (2022). The elegant
complexity of fear in non-human animals. \emph{Emerging Topics in Life
Sciences}, \emph{6}(5), 445--455.
\url{https://doi.org/10.1042/etls20220001}}

\leavevmode\vadjust pre{\hypertarget{ref-2Monfils_2022}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Monfils, M.-H., Lee, H. J., Cofresı́, R. U., \& Gonzales,
R. A. (2022). Friend recollections, and a collection of collaborations
with nadia. \emph{Frontiers in Behavioral Neuroscience}, \emph{16}.
\url{https://doi.org/10.3389/fnbeh.2022.954906}}

\leavevmode\vadjust pre{\hypertarget{ref-3Monfils_2022}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Monfils, M.-H. (2022). The high road to inhibiting fear
memories. \emph{Biological Psychiatry}, \emph{92}(2), 102--103.
\url{https://doi.org/10.1016/j.biopsych.2022.05.005}}

\leavevmode\vadjust pre{\hypertarget{ref-4Hilz_2022}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Hilz, E. N., Olvera, M. E., Jun, D., Chadha, M.,
Gillette, R., Monfils, M.-H., Gore, A. C., \& Lee, H. J. (2022).
Hormonal contraceptives alter amphetamine place preference and
responsivity in the intact female rat. \emph{Behavioral Neuroscience},
\emph{136}(4), 318--329. \url{https://doi.org/10.1037/bne0000520}}

\leavevmode\vadjust pre{\hypertarget{ref-5Agee_2022}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Agee, L. A., Nemchek, V., Malone, C. A., Lee, H. J., \&
Monfils, M.-H. (2021). Appetitive behavior in the social transmission of
food preference paradigm predicts activation of orexin-a producing
neurons in a sex-dependent manner. \emph{Neuroscience}, \emph{481},
30--46. \url{https://doi.org/10.1016/j.neuroscience.2021.11.032}}

\leavevmode\vadjust pre{\hypertarget{ref-6Nemchek_2021}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Nemchek, V., Agee, L. A., Malone, C. A., Raskin, M.,
Seese, S., \& Monfils, M. H. (2021). Altering perceived context:
Transportation cues influence novelty-induced context exploration.
\emph{Frontiers in Behavioral Neuroscience}, \emph{15}.
\url{https://doi.org/10.3389/fnbeh.2021.714927}}

\leavevmode\vadjust pre{\hypertarget{ref-7Hilz_2022}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Hilz, E. N., Lewis, S. M., Olshavsky, M. E., Khoury, E.
S., Gore, A. C., Monfils, M. H., \& Lee, H. J. (2021). Sex differences
in conditioned orienting and the role of estradiol in addiction-related
behaviors. \emph{Behavioral Neuroscience}, \emph{136}(1), 19--29.
\url{https://doi.org/10.1037/bne0000484}}

\leavevmode\vadjust pre{\hypertarget{ref-8Gershman_2021}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Gershman, S. J., Jones, C. E., Norman, K. A., Monfils,
M.-H., \& Niv, Y. (2021). Corrigendum: Gradual extinction prevents the
return of fear: Implications for the discovery of state. \emph{Frontiers
in Behavioral Neuroscience}, \emph{15}.
\url{https://doi.org/10.3389/fnbeh.2021.786900}}

\leavevmode\vadjust pre{\hypertarget{ref-9Lancaster_2020}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Lancaster, C. L., Monfils, M.-H., \& Telch, M. J.
(2020). Augmenting exposure therapy with pre-extinction fear memory
reactivation and deepened extinction: A randomized controlled trial.
\emph{Behaviour Research and Therapy}, \emph{135}, 103730.
\url{https://doi.org/10.1016/j.brat.2020.103730}}

\leavevmode\vadjust pre{\hypertarget{ref-10Blujus_2020}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Blujus, J. K., Prevalska, I., Quevedo, S. F., Auchter,
A., Korthauer, L. E., Dunk, M. M., Monfils, M. H., \& Driscoll, I.
(2020). Updating mechanisms using an olfactory cue were not successful
in improving memory in a rodent model of cognitive aging or in older
adults. \emph{Psychology \& Neuroscience}, \emph{13}(3), 406--423.
\url{https://doi.org/10.1037/pne0000209}}

\leavevmode\vadjust pre{\hypertarget{ref-11Auchter_2020}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Auchter, A. M., Barrett, D. W., Monfils, M. H., \&
Gonzalez-Lima, F. (2020). Methylene blue preserves cytochrome oxidase
activity and prevents neurodegeneration and memory impairment in rats
with chronic cerebral hypoperfusion. \emph{Frontiers in Cellular
Neuroscience}, \emph{14}.
\url{https://doi.org/10.3389/fncel.2020.00130}}

\leavevmode\vadjust pre{\hypertarget{ref-1}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Monfils, M.-H. (2022). CO2 reactivity as a biomarker of
exposure-based therapy non-response: Study protocol. \emph{BMC
Psychiatry}.}

\leavevmode\vadjust pre{\hypertarget{ref-2}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Monfils, M.-H. (2022). Explaining the effectiveness of
fear extinction through latent-cause inference. \emph{Neurons Behavior
Data Analysis \& Theory Journal.}}

\hypertarget{preprints}{%
\subsection{Preprints}\label{preprints}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-1Smits_2022}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Smits, J. A. J., Monfils, M.-H., Otto, M. W., Telch, M.
J., Shumake, J., Feinstein, J. S., Khalsa, S. S., Cobb, A. R., Parsons,
E. M., Long, L. J., McSpadden, B., Johnson, D., Greenberg, A., \&
Consortium, E. T. C. T. (2022). \emph{CO2 reactivity as a biomarker of
exposure-based therapy non-response: Study protocol}.
\url{https://doi.org/10.21203/rs.3.rs-2298817/v1}}

\leavevmode\vadjust pre{\hypertarget{ref-2Agee_2022}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Agee, L. A., Hilz, E. N., Jun, D., Nemchek, V., Lee, H.
J., \& Monfils, M.-H. (2022). \emph{Patterns of arc mRNA expression in
the rat brain following dual recall of fear- and reward-based socially
acquired information}. \url{https://doi.org/10.1101/2021.12.30.474464}}

\leavevmode\vadjust pre{\hypertarget{ref-3Song_2021}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Song, M., Jones, C., Monfils, M.-H., \& Niv, Y. (2021).
\emph{Explaining the effectiveness of fear extinction through
latent-cause inference}. \url{https://doi.org/10.31234/osf.io/2fhr7}}

\leavevmode\vadjust pre{\hypertarget{ref-4Hilz_2021}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Hilz, E. N., Agee, L. A., Jun, D., Monfils, M. H., \&
Lee, H. J. (2021). \emph{Expression patterns of arc mRNA after renewal
of appetitive behavior in female rats}.
\url{https://doi.org/10.1101/2021.07.20.453088}}

\leavevmode\vadjust pre{\hypertarget{ref-5Hilz_2021}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Hilz, E. N., Olvera, M., Jun, D., Chadha, M., Gillette,
R., Monfils, M.-H., Gore, A. C., \& Lee, H. J. (2021). \emph{Hormonal
contraceptives alter amphetamine place preference and responsivity in
the intact female rat}. \url{https://doi.org/10.1101/2021.07.28.454029}}

\hypertarget{books}{%
\subsection{Books}\label{books}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-1}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Monfils, M.-H. (2023). \emph{Social beasts: Learning
vicariously to flexibly adapt to a changing world.} Princeton University
Press.}

\hypertarget{book-chapters}{%
\subsection{Book Chapters}\label{book-chapters}}

\hypertarget{bibliography}{}
\leavevmode\vadjust pre{\hypertarget{ref-1}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Monfils, M.-H. (2022). Reconsolidation and fear
extinction: An update. In \emph{Current topics in behavioral
neurosciences (CTBN). Mohamed milad and seth norrholm, editors.}}

\leavevmode\vadjust pre{\hypertarget{ref-2}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Monfils, M.-H. (2021). How can intrusive thinking be
conceptualized at the level of psychological mechanisms? In \emph{Ernst
strungmann forum book intrusive thinking across neuropsychological
disorders.}}

\leavevmode\vadjust pre{\hypertarget{ref-3}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Monfils, M.-H. (2021). Neuropsychological mechanisms of
intrusive thinking. In \emph{In ernst strungmann forum book intrusive
thinking across neuropsychological disorders}.}

\hypertarget{professional-presentations}{%
\section{Professional Presentations}\label{professional-presentations}}

\begin{cventries}
    \cventry{Cambridge University}{Individual differences and social transfer of knowledge.}{}{2021}{}\vspace{-4.0mm}
    \cventry{Wayne State University}{Assessing individual differences to optimize fear attenuation.}{}{2021}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{conference-abstracts}{%
\section{Conference Abstracts}\label{conference-abstracts}}

\hypertarget{honors}{%
\section{Honors}\label{honors}}

\begin{cventries}
\end{cventries}

\hypertarget{funding}{%
\section{Funding}\label{funding}}

\begin{cventries}
    \cventry{Funding: \$1,964,345}{Reducing alcohol-seeking behavior in a rat model of alcohol dependence- Co-I  (pending; 1st percentile)}{NIH, }{2022 - 2027}{}\vspace{-4.0mm}
    \cventry{Funding: \$763,817}{1/2: CO2 Reactivity as a Biomarker of Non-response to Exposure-based Therapy}{NIMH, R01MH125951}{2022 - 2027}{}\vspace{-4.0mm}
    \cventry{Funding: \$800,000}{Influence of shared experience on relational dynamics and vicarious learning}{Directorate for Social, Behavioral \& Economic Sciences, 2141102}{2022 - 2025}{}\vspace{-4.0mm}
    \cventry{Funding: \$472,297}{Disambiguating networks and factors that promote social transmission of information in rats}{Directorate for Social, Behavioral \& Economic Sciences, 1748911}{2018 - 2021}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{service}{%
\section{Service}\label{service}}

\begin{cventries}
    \cventry{Undergraduate Mentor}{The University of Texas at Austin}{Austin, 
US}{2022 -
present}{}\vspace{-4.0mm}
    \cventry{Grant Reviewer}{The University of Texas at Austin}{Austin, 
US}{2022 -
present}{}\vspace{-4.0mm}
    \cventry{Member}{The University of Texas at Austin}{Austin, 
US}{2022 -
present}{}\vspace{-4.0mm}
    \cventry{Chair}{The University of Texas at Austin}{Austin, 
US}{2022 -
present}{}\vspace{-4.0mm}
    \cventry{Member}{The University of Texas at Austin}{Austin, 
US}{2021 -
present}{}\vspace{-4.0mm}
    \cventry{Advisory Council Member}{The University of Texas at Austin}{Austin, 
US}{2020 -
present}{}\vspace{-4.0mm}
    \cventry{Associate Chair for Research and Operations}{The University of Texas at Austin}{Austin, 
US}{2019 -
present}{}\vspace{-4.0mm}
    \cventry{Executive Committee Member-Psychology}{The University of Texas at Austin}{Austin, 
US}{2019 -
present}{}\vspace{-4.0mm}
    \cventry{Member}{The University of Texas at Austin}{Austin, 
US}{2019 -
present}{}\vspace{-4.0mm}
    \cventry{Chair of Animal Research Center Faculty Advisory Committee}{The University of Texas at Austin}{Austin, 
US}{2017 -
present}{}\vspace{-4.0mm}
    \cventry{Mentor}{The University of Texas at Austin}{Austin, 
US}{2022 -
2023}{}\vspace{-4.0mm}
    \cventry{Grant Reviewing}{Swiss National Science Foundation}{Bern, 
CH}{2021 -
2022}{}\vspace{-4.0mm}
    \cventry{CoLA COVID 19 response; Research Reopening Committee}{The University of Texas at Austin}{Austin, 
US}{2020 -
2022}{}\vspace{-4.0mm}
    \cventry{CoLA COVID 19 response; Research Reopening Building coordinator for SEA Building}{The University of Texas at Austin}{Austin, 
US}{2020 -
2022}{}\vspace{-4.0mm}
    \cventry{}{NIMH}{Bethesda, 
US}{2018 -
2022}{}\vspace{-4.0mm}
    \cventry{Science Reports}{University of Texas at Austin}{Austin, 
US}{2017 -
2022}{}\vspace{-4.0mm}
    \cventry{Frontiers in Behavioral Neuroscience}{University of Texas at Austin}{Austin, 
US}{2010 -
2022}{}\vspace{-4.0mm}
    \cventry{Executive Committee Member-Institute for Neuroscience}{The University of Texas at Austin}{Austin, 
US}{2018 -
2021}{}\vspace{-4.0mm}
    \cventry{Graduate Adviser}{The University of Texas at Austin}{Austin, 
US}{2018 -
2021}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{mentoring-and-teaching}{%
\section{Mentoring and Teaching}\label{mentoring-and-teaching}}

\hypertarget{mentoring}{%
\subsection{Mentoring}\label{mentoring}}

\begin{cventries}
    \cventry{Undergraduate Honors student}{Miriam Ortega}{}{NA -
present}{}\vspace{-4.0mm}
    \cventry{Undergraduate Mentor}{Michael Pasala}{}{2022 -
present}{}\vspace{-4.0mm}
    \cventry{Undergraduate Student}{Grace Wulffraat}{}{2021 -
2023}{}\vspace{-4.0mm}
    \cventry{Committee Member}{Tyler Milewski}{}{2022 -
2022}{}\vspace{-4.0mm}
    \cventry{Graduate Mentor}{Sydney Seese}{}{2020 -
2022}{}\vspace{-4.0mm}
    \cventry{Dissertation Supervisor}{Kylee Smith}{}{2018 -
2022}{}\vspace{-4.0mm}
    \cventry{Supervisor}{Marissa Raskin}{}{2018 -
2022}{}\vspace{-4.0mm}
    \cventry{Undergraduate Student}{Sun Chong}{}{2020 -
2021}{}\vspace{-4.0mm}
    \cventry{Graduate Mentor}{Victoria Nemchek}{}{2019 -
2021}{}\vspace{-4.0mm}
    \cventry{Dissertation Supervisor}{Laura Agee}{}{2015 -
2021}{}\vspace{-4.0mm}
    \cventry{Committee Member}{Emily Hilz}{}{2015 -
2021}{}\vspace{-4.0mm}
\end{cventries}

~

\hypertarget{teaching}{%
\subsection{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Instructor}{Psychology 371}{}{2019 -
2022}{}\vspace{-4.0mm}
\end{cventries}



\end{document}
